DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-06 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
ase2017

There are various ways to model control systems.  Two common ways to
represent the dynamics of such systems are transfer functions and
state-space equations (difference or differential equations).  In this
paper, we consider systems with a single input and a single output (SISO)
given either as transfer functions or state-space linear time-invariant
(LTI) models.  LTI models are a common sub-class, and are frequently used in
cyber-physical systems (e.g., in robotics, smart grids, power plants, and
avionics).  A discretized plant or a digital controller is, in generally,
given as follows when using a transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{a_{0}+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
In this representation, $z^{-1}$ is called the backward-shift operator;
$A(z)$ and $B(z)$ are the denominator and numerator polynomials; and $N$ and
$M$ are the order of the denominator and numerator polynomials, respectively.

@@

%The digital controllers synthesized by \tool are all stable using the MATLAB step response
%as a validation procedure, which means that our results are reliable for control engineers. 
The synthesized controllers are also confirmed to be safe outside of our model
representation using MATLAB, which means that our results are reliable for control engineers. 
In particular, we unfold the system dynamics up to a given depth, 
compute the system input and output via the feedback matrix, and then check the states bounds.
 A link to the full experimental environment, including the scripts, benchmarks, 
 videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}

>>>>

There are various ways to model control systems.  Two common ways to
represent the dynamics of such systems are transfer functions and
state-space equations (difference or differential equations).  In this
paper, we consider systems with a single input and a single output (SISO)
given either as transfer functions or state-space linear time-invariant
(LTI) models.  LTI models are a common sub-class, and are frequently used in
cyber-physical systems (e.g., in robotics, smart grids, power plants, and
avionics).  A discretized plant or a digital controller is, in general,
given as follows when using a transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{a_{0}+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
In this representation, $z^{-1}$ is called the backward-shift operator;
$A(z)$ and $B(z)$ are the denominator and numerator polynomials; and $N$ and
$M$ are the order of the denominator and numerator polynomials, respectively.

@@

%The digital controllers synthesized by \tool are all stable using the MATLAB step response
%as a validation procedure, which means that our results are reliable for control engineers. 
The synthesized controllers are also confirmed to be safe outside of our model
representation using MATLAB, which means that our results are reliable for control engineers. 
In particular, the safety of controllers may be checked in computing the infinity norm of states, {\it i.e.}, the product between $l_{\infty}$ norm of initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) and the $l_{1}$ norm of ($\vert\vert{\bar{A}}\vert\vert_{1}=\max\limits_{j}{\sum\limits_{i=1}^{m} \vert \bar{a}_{ij} \vert}$, where $\bar{A}=A-BK$). This is a conservative safety checking that is based in a sufficient condition~\cite{toscano2013structured}. An alternative (and less conservative)  is to unfold the system dynamics up to a given depth, with the initial state equal to its maximum value, and compute the system input and output via the feedback matrix, and then check the states bounds.
 A link to the full experimental environment, including the scripts, benchmarks, 
 videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}
